### 2023-10-04 main.tex
fix
N2 correlations

@@

	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\frac{\beta_{a}}{|\beta|}\right)^{\xi_{a}^{L+1}}

>>>>

\\ \\
\textbf{Remark}: If we stop distinguishing the types of particles we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite{frassek2020eigenstates}. Indeed, introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes
	\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=&\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}
	\\&\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
We observe that, at most $q$ factors do survive in the product over $k$. Moreover, for a fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
	\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}\dt
For any $q\in\{1,\ldots,m\}$, we can introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,m\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$ and write 
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{m}=q\}}\prod_{k=1}^{m}\left(L+2-y_{k}-\sum_{i=k}^{m}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\left(L+2-y_{\ell_{k}}-(q-k+1)\right)\dt
Moreover, observing that 
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}
All in all we obtain 
\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{q=0}^{m}(\alpha-\beta)^{q}\beta^{m-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq m}\prod_{k=1}^{q}\frac{\left(L+1-y_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt
that is exactly equation (4.26) of \cite{frassek2020eigenstates}.

@@

	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\frac{\beta_{a}}{|\beta|}\right)^{\xi_{a}^{L+1}}
